Technique for \earlywarning\ detection of compact binary coalescence and its implication for multi-messenger astronomy

### 2011-06-03 inspiral_svd.tex
Added acknowledgement for my fellowship
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@862 ccdd05d5-56c1-461a-bf98-85f6876523b4
Removed backup title
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@863 ccdd05d5-56c1-461a-bf98-85f6876523b4
Fixed some accent errors in author addresses
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@864 ccdd05d5-56c1-461a-bf98-85f6876523b4
Added editorial note about addresses for co-authors
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@867 ccdd05d5-56c1-461a-

% Backup title.
%\title[LLOID]{Method for early-warning detection of compact binary coalescence.}

@@

\address{$^1$ Canadian Institute for Theoretical Astrophysics, Toronto, ON,
Canada}
\address{$^2$  D\'{e}partement de physique, \'{E}cole Normale Sup\'{e}rieure de Cachan, 61
Avenue du Pr\'{e}sident Wilson, 94235 Cachan Cedex, France}
\address{$^3$ LIGO Laboratory - California Institute of Technology, Pasadena,
CA, USA} 
\address{$^4$ Facultat de Física, Universitat de València, E-46100 Burjassot,
Spain} 
\address{$^5$ The University of Texas at Austin, Austin, TX, USA}
\address{$^6$ Perimeter Institute for Theoretical Physics, Waterloo, ON,
Canada} 
\address{$^7$ Department of Physics and Astronomy, Barnard College, Columbia
University, New York, NY 10027, USA} 
\address{$^8$ Albert-Einstein-Institut, Max-Planck-Institut f\"{u}r
Gravitationphysik, Hannover, Germany} 
\address{$^9$ Leibniz Universit\"{a}t Hannover, Hannover, Germany}
\address{$^{10}$ Ryerson University, Toronto, ON, Canada}

@@

\ack{\LIGO\ was constructed by the California Institute of Technology and
Massachusetts Institute of Technology with funding from the National Science
Foundation and operates under cooperative agreement
\textsc{phy}-\oldstylenums{0107417}. CH would like to thank Ilya Mandel for
many discussions about rate estimates and the prospects of early detection.  CH
would also like to thank Patrick Brady for countless fruitful conversations
about low latency analysis methods.  NF would like to thank Alessandra Corsi
for illuminating discussions on astronomical motivations.

>>>>

@@

\editorial{We have only Institution, City, State, Country for some co-authors.  Can we get rid of the full addresses, or is this at the discretion of the co-authors?}
\address{$^1$ Canadian Institute for Theoretical Astrophysics, Toronto, ON,
Canada}
\address{$^2$  D\'{e}partement de physique, \'{E}cole Normale Sup\'{e}rieure de Cachan, 61
Avenue du Pr\'{e}sident Wilson, 94235 Cachan Cedex, France}
\address{$^3$ LIGO Laboratory - California Institute of Technology, Pasadena,
CA, USA} 
\address{$^4$ Facultat de F\'{i}sica, Universitat de Val\`{e}ncia, E-46100 Burjassot,
Spain} 
\address{$^5$ The University of Texas at Austin, Austin, TX, USA}
\address{$^6$ Perimeter Institute for Theoretical Physics, Waterloo, ON,
Canada} 
\address{$^7$ Department of Physics and Astronomy, Barnard College, Columbia
University, New York, NY 10027, USA} 
\address{$^8$ Albert-Einstein-Institut, Max-Planck-Institut f\"{u}r
Gravitationphysik, Hannover, Germany} 
\address{$^9$ Leibniz Universit\"{a}t Hannover, Hannover, Germany}
\address{$^{10}$ Ryerson University, Toronto, ON, Canada}

@@

\ack{\LIGO\ was constructed by the California Institute of Technology and
Massachusetts Institute of Technology with funding from the National Science
Foundation and operates under cooperative agreement
\textsc{phy}-\oldstylenums{0107417}.  This research is supported by the National Science Foundation through a Graduate Research Fellowship to LS.  CH would like to thank Ilya Mandel for
many discussions about rate estimates and the prospects of early detection.  CH
would also like to thank Patrick Brady for countless fruitful conversations
about low latency analysis methods.  NF would like to thank Alessandra Corsi
for illuminating discussions on astronomical motivations.
